\documentclass[a4paper,10pt]{article}

\title{Kaptan Test Cases}
\author{Semen Cirit}

\renewcommand{\labelenumi}{\arabic{enumi}.}
\renewcommand{\labelenumii}{\arabic{enumi}.\arabic{enumii}.}
\renewcommand{\labelenumiii}{\arabic{enumi}.\arabic{enumii}.\arabic{enumiii}.}
\renewcommand{\labelenumiv}{\arabic{enumi}.\arabic{enumii}.\arabic{enumiii}.\arabic{enumiv}.}

\begin{document}

\maketitle

\begin{enumerate}

\item Try Kaptan for all resolutions. 1440*900 to 800*600. 

\item Create a new user, and open this account.
\begin{enumerate}
    \item Can kaptan open immediately?
    \item After starting kaptan

          Execute the following command:
\begin{verbatim}
    # vi ~/.kde4/share/config/kaptanrc
\end{verbatim} 
        Observe that RunOnStart is equal to False.

    \item Behaviour of the mouse
    \begin{enumerate}
        \item Choose double click.

            Observe the situation.
        \item Choose single click

            Observe the situation.

        \item Choose left hand

            Observe the situation.
        \item Choose right hand

            Observe the situation.

        \item Enable reverse scrolling,

            Observe the situation.
    \end{enumerate}
\end{enumerate}

\item All of the changes below can be observed when kaptan finished. Each situation should be observed separetely.
(For each situation, kaptan can be started from console by typing the command "kaptan")
    \begin{enumerate}
    \item Theme and desktop type
        \begin{enumerate}
        \item Select each theme and observe each situation.
        \item Observe the situation when Desktop is selected for desktop type.
        \item Observe the situation when  Folder view is selected for desktop type.
        \item Change number of desktops and observe the stuation.
        \end{enumerate}

    \item Menu Style.
        \begin{enumerate}
        \item Observe each situation.
        \end{enumerate}

    \item Wallpaper
        \begin{enumerate}
        \item Try to choose a wallpaper
            \begin{enumerate}
            \item From the screen of kaptan, observe the situation.
            \item From the system, observe the situation.
            \end{enumerate}
        \item Not try to change wallpaper, observe the situation.
        \end{enumerate}

    \item Nepomuk Semantic Desktop
        \begin{enumerate}
        \item Enable it and  observe the situation.
        \item Disable it and  observe the situation.
        \end{enumerate}

    \item Network configuration
        \begin{enumerate}
        \item Apply the test cases from network-manager.
        \end{enumerate}

    \item Package manager configuration
        \begin{enumerate}
        \item Updates
            \begin{enumerate}
            \item Enable show package manager on system tray.
                Observe that it is on system tray.
            \item Disable show package manager on system tray.
                Observe that it is not on system tray.
            \item Enable control updates periodicly and give a short observable period.
                Observe that package manager gives warnings for updates from system tray.
            \item Disable control updates periodicly and give a short observable period.
                Observe that package manager doesn't give warnings for updates from system tray.
            \end{enumerate}
        \end{enumerate}

        \begin{enumerate}
        \item Repository
            \begin{enumerate}
            \item Enable contrib repository 
                Then type command 
\begin{verbatim}
    # pisi lr 
\end{verbatim}
                 Observe that this repository is an output of this command.
            \item Disable contrib repository
                Then type command 
\begin{verbatim}
    # pisi lr 
\end{verbatim}
                 Observe that this repository is not an output of this command.
            \end{enumerate}
        \end{enumerate}

    \item Pardus settings
        \begin{enumerate}
        \item Try to start systems settings
        \item Try to start user groups and help pages.
        \end{enumerate}

    \item Smolt hardware profiler
        \begin{enumerate}
        \item Enable smolt 
            Observe that the computer hardware profile can be sent to smolt.pardus.org.tr
        \end{enumerate}
    \end{enumerate}
\end{enumerate}

\end{document}
