\documentclass[a4paper,10pt]{article}
\usepackage[left=1cm,top=1cm,right=2cm,bottom=2cm]{geometry}
\title{Boot Manager Test Cases}
\author{Semen Cirit}

\renewcommand{\labelenumi}{\arabic{enumi}.}
\renewcommand{\labelenumii}{\arabic{enumi}.\arabic{enumii}.}
\renewcommand{\labelenumiii}{\arabic{enumi}.\arabic{enumii}.\arabic{enumiii}.}
\renewcommand{\labelenumiv}{\arabic{enumi}.\arabic{enumii}.\arabic{enumiii}.\arabic{enumiv}.}

\begin{document}

\maketitle

\begin{enumerate}
    \item Try to open boot-manager from systemsettings. 
    \item Try to open boot-manager from Kmenu
    \item Add a new bootable system from "add new" dropdown menu.
    \begin{enumerate}
        \item For all system options try to left empty the textbox(es) and then observe that they give a warning about it.

        \item For Windows give a title and write the partition of related windows system and then click "ok".

            Observe the results with using the below note.


\item Xen or Linux 
\begin{enumerate}
    \item Give a title
    \item Write the partition of related system.
    \item Write the kernel of related system.
    \item Write the ramdisk file (initramfs) of related system.
    \item Write some related boot option.
    \item Then click "ok".

          Observe the results with using the below note.

\end{enumerate}

\item For memtest give a title then click ok.

    Observe the results with using the below note.

    \end{enumerate}
\item Try to change timeout and then observe it with using the below note.
\end{enumerate}

\subsection*{Note:}
    \begin{enumerate}
    \item Observe each result from /boot/grub/grub.conf, then restart computer and try each situation.
    \item Looking for related partition
        \begin{enumerate}
            \item Execute the following command:
            \begin{verbatim}
                # fdisk -l
            \end{verbatim}
        \end{enumerate}
    \item Looking for kernel and initramfs
        \begin{enumerate}
            \item Execute the following command:
            \begin{verbatim}
                # ls /boot
            \end{verbatim}
        \end{enumerate}
    \end{enumerate}


\end{document}

