\documentclass[a4paper,10pt]{article}
\usepackage[left=1cm,top=1cm,right=2cm,bottom=2cm]{geometry}
\renewcommand{\labelenumi}{\arabic{enumi}.}
\renewcommand{\labelenumii}{\arabic{enumi}.\arabic{enumii}.}
\renewcommand{\labelenumiii}{\arabic{enumi}.\arabic{enumii}.\arabic{enumiii}.}
\renewcommand{\labelenumiv}{\arabic{enumi}.\arabic{enumii}.\arabic{enumiii}.\arabic{enumiv}.}

\title{Disk Manager Test Cases}
\author{Semen Cirit}

\begin{document}

\maketitle
\begin{enumerate}

\item Try to open disk-manager from system settings.
\item Try to open disk-manager from Kmenu.

\item Mounting an external usb stick or an other similar device. (Initially the disk not mounted) 
    \begin{enumerate}
        \item Execute the following command:
            \begin{verbatim}
                # mount
            \end{verbatim}
            Observe that this disk is not mounted to anywhere. 

	\item Observe also that the other mounted disks that seen on the disk-manager are mounted properly.  

    \item Try to mount this disk to home directory.
          Observe whether the disk manager gives a warning message about this unvalid mount point.
    \item Try to mount this disk
        \begin{enumerate}
            \item Type an appropriate mount point. For example "/mnt/sample"
            \item Give an appropriate filesystem.
            \item Give the appropriate options for the mounted device.
            \item Apply it.
            \item Execute the following command:
            \begin{verbatim}
                # mount
            \end{verbatim}
                Observe that it is mounted properly according to your directions given.
        \end{enumerate}

    \item Try to change the mount point of this disk
        \begin{enumerate}
            \item Execute the following command:
            \begin{verbatim}
                # mount
            \end{verbatim}
            Observe whether the disk manager gives a warning that the disk is already mounted.
        \end{enumerate}

    \item Try to change the filesystem type
        \begin{enumerate}
            \item Execute the following command:
            \begin{verbatim}
                # blkid
            \end{verbatim}
                  For a selected device, observe that the default filesystem type on disk-manager is the same with the output of "blkid".
            \item Change the filesystem type:
                  Observe that if this filesystem type is not suitable with this device, disk-manager gives a warning message about it.
        \end{enumerate}

    \item Try to add an option for mounting
        \begin{enumerate}
          \item When the option part is empty try to click OK button.
                Observe that it gives a warning about it.
          \item If you add some option to option part,
                Observe that the output of the command "mount" contains this option for the related disk.
        \end{enumerate}
    \end{enumerate}

\item Try to change the mount point of the root partition

      Observe that it gives a warning about it can not remount.

        \textbf{Note :} the mount point of root should be "/".

\item Observe whether an extended partition listed on disk-manager screen. (Normally it can not be listed).

\item Cancel the autorization window.

After canceled the operation, observe that the information about the disk remain in previous state.

\item When you make some operation on disk manager, select always remember autorization.

Make an other operation, observe that the password is ignored.

\end{enumerate}

\end{document}
