\documentclass[a4paper,10pt]{article}
\usepackage[turkish]{babel}
\usepackage[utf8]{inputenc}
\usepackage[left=1cm,top=1cm,right=2cm,bottom=2cm]{geometry}

\title{Editor Component Testcases}
\author{Semen Cirit}

\renewcommand{\labelenumi}{\arabic{enumi}.}
\renewcommand{\labelenumii}{\arabic{enumi}.\arabic{enumii}.}
\renewcommand{\labelenumiii}{\arabic{enumi}.\arabic{enumii}.\arabic{enumiii}.}
\renewcommand{\labelenumiv}{\arabic{enumi}.\arabic{enumii}.\arabic{enumiii}.\arabic{enumiv}.}

\begin{document}

\maketitle

\subsection*{Ed}

There is an example ed session below. You can test ed, applying these writtens, after you run ed.

\begin{verbatim}
a
ed is a standard text editor.
This is second line.
.
2i

.
%l
ed is a standartd text editor.$
$
This is second line.$
3s/second/third/
,l
ed is a standard text editor.$
$
This is third line.$
w text.txt
54
q
\end{verbatim}
Observe that it written below an information at text.txt.
\begin{verbatim}
ed is a standard text editor.

This is second line.
\end{verbatim}


\subsection*{Emacs}
\begin{enumerate}
\item After Emacs package installation:

Open emacs from Kmenu

Observe that it open correctly.

\item After color-theme package installation:

save .emacs file under home directory using below command. 
\begin{verbatim}
# wget http://cekirdek.pardus.org.tr/~semen/dist/test/editor/.emacs 
\end{verbatim}

After you open Emacs application, run below command from emacs command line.
\begin{verbatim}
 M-x color-theme-aalto-dark
\end{verbatim}

Observe that theme changed correctly.

\item After emacs-muse package installation:

save .emacs file under home directory using below command.
\begin{verbatim}
# wget http://cekirdek.pardus.org.tr/~semen/dist/test/editor/.emacs 
\end{verbatim}

after you open Emacs application,  type the below command then press tab button in order to list muse different muse options.
\begin{verbatim}
 M-x muse-
\end{verbatim}


\end{enumerate}


\subsection*{Joe}

After Joe package installation, run below command from console.

\begin{verbatim}
 # joe example.txt
\end{verbatim}

Write below information with joe.
\begin{verbatim}
this is an example vi test.
this is second line.
\end{verbatim}

Save the file using below command, and exit.
\begin{verbatim}
C-kd key for saving file.
C-c for exitin from file.
\end{verbatim}


observe that file is saved correctly using below command.
\begin{verbatim}
# joe example.txt 
\end{verbatim}

\subsection*{Vi sub component}

\begin{enumerate}

\item Vi package

after the package installation, run below command from console.

\begin{verbatim}
 # vi example.txt
\end{verbatim}

write below informations with vi.
\begin{verbatim}
This is an example vi test.
This is second line.
\end{verbatim}

save the file using below commands with vi editor's command line.
\begin{verbatim}
:w key for saving file.
:q key for exiting from file.
\end{verbatim}

observe that file is saved correctly using below command.
\begin{verbatim}
# vi ornek.txt 
\end{verbatim}

\item vim-colorschemes package

run beleow file.
\begin{verbatim}
# vi example.py
\end{verbatim}

Then run vi command:
\begin{verbatim}
:colorscheme Blacksea
\end{verbatim}

Observe that color theme is changed.


\item after gvim package installation:

run below commands and observe that a vi window opened.
\begin{verbatim}
 # eview
 # evim
\end{verbatim}

then apply editor-eng.pdf vi test for these windows.

\item After zile package installation:
Run below command and observe that a new vi window opened.
\begin{verbatim}
 # zile
\end{verbatim}


\end{enumerate}

\end{document}

