\documentclass[a4paper,10pt]{article}
\usepackage[left=1cm,top=2cm,right=2cm,bottom=1cm]{geometry}

\title{History Manager Test Cases}
\author{Semen Cirit}

\renewcommand{\labelenumi}{\arabic{enumi}.}
\renewcommand{\labelenumii}{\arabic{enumi}.\arabic{enumii}.}
\renewcommand{\labelenumiii}{\arabic{enumi}.\arabic{enumii}.\arabic{enumiii}.}
\renewcommand{\labelenumiv}{\arabic{enumi}.\arabic{enumii}.\arabic{enumiii}.\arabic{enumiv}.}

\begin{document}

\maketitle

\begin{enumerate}
\item Try to open history manager from system settings.
\item Try to open history manager from Kmenu.
\item Try to Take snapshot	
\begin{enumerate}
    \item Install or remove a package from package manager.
    \item Push take snapshot button from history manager.
    \item Observe that after taking snapshot whether the history manager screen can be refreshed and show new changes.
\end{enumerate}

\item Try to push details button for a date.

    Execute the following command:
\begin{verbatim}
    $ pisi hs
\end{verbatim} 

    Compare the last changes with history manager according to related date. 

\item Try to push Show operation plan button for a date.
    Execute the following command:
\begin{verbatim}
     $ pisi hs
\end{verbatim} 
    Compare the last changes with history manager for the related date.

    Observe that the package(s) will be updated, installed or removed correctly.

\item Try to push Take Changes Back button for a date.

        After taking changes back 
\begin{enumerate}
        \item Observe whether the history manager screen can be refreshed.
        \item Push the show operations button of the related time that you had taken the operation(s) back.

              Observe that operation(s) had been removed from the show operation plan list.
     	\item Execute the below command:
\begin{verbatim}
    $ pisi hs
\end{verbatim} 

            Compare the last changes with history manager.

            Observe that the operations that had taken back are listed correctly.
\end{enumerate}

\item Cancel the authorization window, when you try to do some operation.

After the operation canceled, observe that the situation of the manager remain in its early state.

\item During an operation, try to select always remember password.

Make an operation from history manager.

Observe that the authorization is ignored, when the operation has been done.
\end{enumerate}

% \end{enumerate}

\end{document}
