\documentclass[a4paper,10pt]{article}
\usepackage[left=1cm,top=1cm,right=2cm,bottom=2cm]{geometry}
\title{Kaptan Test Cases}
\author{Semen Cirit}

\renewcommand{\labelenumi}{\arabic{enumi}.}
\renewcommand{\labelenumii}{\arabic{enumi}.\arabic{enumii}.}
\renewcommand{\labelenumiii}{\arabic{enumi}.\arabic{enumii}.\arabic{enumiii}.}
\renewcommand{\labelenumiv}{\arabic{enumi}.\arabic{enumii}.\arabic{enumiii}.\arabic{enumiv}.}

\begin{document}

\maketitle

\begin{enumerate}

\item Try Kaptan for all resolutions. 1440*900 to 800*600.

Observe that kaptan can open for each resolution.

\item Try Kaptan with 4:3 and 16:9 screen.

Observe that kaptan can open for each resolution.

\item Create a new user, and open this account.
\begin{enumerate}
    \item Can kaptan open immediately?

    \item After starting kaptan

          Execute the following command:
\begin{verbatim}
    # vi ~/.kde4/share/config/kaptanrc
\end{verbatim} 
        Observe that RunOnStart is equal to False.

    \item Behaviour of the mouse
    \begin{enumerate}
        \item Choose double click.

            Observe the situation.
        \item Choose single click

            Observe the situation.

        \item Choose left hand

            Observe the situation.
        \item Choose right hand

            Observe the situation.

        \item Enable reverse scrolling,

            Observe the situation.
    \end{enumerate}
\end{enumerate}

\item All of the changes below can be observed when kaptan finished. Each situation should be observed separetely.
(For each situation, kaptan can be started from console by typing the command "kaptan")
    \begin{enumerate}
    \item Theme and desktop type
        \begin{enumerate}
        \item Select each theme and observe each situation.

        After the operations of Kaptan finish, observe that these themes selected.

        The selected theme can be observed from System Settings $\rightarrow$ Appearance $\rightarrow$ Style $\rightarrow$ Widget Style.

        
        The selected theme can be observed from System Settings $\rightarrow$ Icons.


        The selected theme can be observed from System Settings $\rightarrow$ Windows $\rightarrow$ Windows Decoration.
        
        \item Observe the situation when Desktop is selected for desktop type.

        \item Observe the situation when  Folder view is selected for desktop type.

        These two type can be observed from right click on desktop $\rightarrow$ Appearance Settings 
        $\rightarrow$ Desktop Activity.

        \item Change number of desktops and observe the stuation.

        After Kaptan operations finish observe that the desktop number. 
        \end{enumerate}

    \item Select a menu Style.

    Observe that this style is selected after Kaptan is finished.

    \item Wallpaper
        \begin{enumerate}
        \item Try to choose a wallpaper
            \begin{enumerate}
            \item From the screen of kaptan, observe the situation.
            \item From the system, observe the situation.
            \end{enumerate}
        \item Not try to change wallpaper, observe the situation.
        \end{enumerate}

    \item Nepomuk Semantic Desktop
        \begin{enumerate}
        \item Enable it and  observe the situation.
        \item Disable it and  observe the situation.

        If it is enabled, its icon should be on system tray.
        \end{enumerate}

    \item Network configuration
        \begin{enumerate}
        \item Apply the test cases from network-manager.
        \end{enumerate}

    \item Package manager configuration
        \begin{enumerate}
        \item Updates
            \begin{enumerate}
            \item Enable show package manager on system tray.

                Observe that it is on system tray.
            \item Disable show package manager on system tray.

                Observe that it is not on system tray.
            \item Enable control updates periodicly and give a short observable period.

                Observe that package manager gives warnings for updates from system tray.
            \item Disable control updates periodicly and give a short observable period.

                Observe that package manager doesn't give warnings for updates from system tray.
            \end{enumerate}
        \end{enumerate}

        \begin{enumerate}
        \item Repository
            \begin{enumerate}
            \item Enable contrib repository 
                Then type command 
\begin{verbatim}
    # pisi lr 
\end{verbatim}
                 Observe that this repository is an output of this command.
            \item Disable contrib repository
                Then type command 
\begin{verbatim}
    # pisi lr 
\end{verbatim}
                 Observe that this repository is not an output of this command.
            \end{enumerate}
        \end{enumerate}

    \item Pardus settings
        \begin{enumerate}
        \item Try to start systems settings
        
        \item Try to start user groups and help pages.

        \end{enumerate}

    \item Smolt hardware profiler
        \begin{enumerate}
        \item Enable smolt 
            Observe that the computer hardware profile can be sent to smolt.pardus.org.tr
        \end{enumerate}
    \end{enumerate}
\end{enumerate}

\end{document}
