\documentclass[a4paper,10pt]{article}
\usepackage[turkish]{babel}
\usepackage[utf8]{inputenc}
\usepackage[left=1cm,top=1cm,right=2cm,bottom=2cm]{geometry}

\title{Library Test Cases}
\author{Semen Cirit}

\renewcommand{\labelenumi}{\arabic{enumi}.}
\renewcommand{\labelenumii}{\arabic{enumi}.\arabic{enumii}.}
\renewcommand{\labelenumiii}{\arabic{enumi}.\arabic{enumii}.\arabic{enumiii}.}
\renewcommand{\labelenumiv}{\arabic{enumi}.\arabic{enumii}.\arabic{enumiii}.\arabic{enumiv}.}

\begin{document}

\maketitle
\begin{enumerate}
\item  Following packages subject to installation test:
\begin{verbatim}
yazpp
xmlsec
libftdi
libp11
libuuid
cddlib
\end{verbatim}

\item After installation qimageblitz pacakage:

Open the below image with blitztest application and observe that the effect test is done without any problem.
\begin{verbatim}
 # wget http://cekirdek.pardus.org.tr/~semen/dist/test/office/openoffice/test_oodraw.png
 # blitztest
\end{verbatim}


\item After installation tre package:

Do multimedia-eng.pdf streamripper package test.

\item After installation gstreamer, gst-plugin-ugly, gst-plugin-bad, gst-plugin-base and gst-ffmeg packages:

Follow System Settings $\rightarrow$ Multimedia $\rightarrow$ gstreamer path:

Run the below files with dragon player ve kaffein and observe they are running without any problem.
\begin{verbatim}
 # wget http://cekirdek.pardus.org.tr/~semen/dist/test/multimedia/video/cokluortam/niceday.asf
 # wget http://cekirdek.pardus.org.tr/~semen/dist/test/multimedia/video/cokluortam/MPEG-1_with_VCD_extensions.mpeg
 # wget http://cekirdek.pardus.org.tr/~semen/dist/test/multimedia/video/cokluortam/Lake_dance_XviD.AVI
\end{verbatim}

\item After installation exempi and yaz packages:

Do office-eng.pdf tellico package test.

\item After installation eet and eina packages: 
\begin{itemize}
 \item [for 2008] İnstall edb package. Observe that the below commands run without any problem.
\begin{verbatim}
 # wget http://cekirdek.pardus.org.tr/~semen/dist/test/library/test_edb
 # chmod 755 test_edb
 # ./test_edb
 # edb_ed test.db get /foo/theme str
\end{verbatim}
\item [for 2009] Do library-eng.pdf qedje package test.
\end{itemize}

\item After installation qedje package:

Run the below commands and observe that they run without any problem.
\begin{verbatim}
# qedje_viewer
\end{verbatim}

\item After installation geoip package:

Run the below command. Observe that it returns a result like "GeoIP Country Edition: US, United States".
\begin{verbatim}
# geoiplookup www.google.com 
\end{verbatim}

\item After installation nss and nspr packages:

Do network-eng.pdf firefox and office-enf.pdf openoffice packages tests.

\item After installation openexr package:
\begin{itemize}
 \item Do multimedia-eng.pdf gimp, digikam ve imagemagick packages tests.
 \item Observe that the image files, which locate in below archive file, can open without any problem with gwenview.
  \begin{verbatim}
   http://cekirdek.pardus.org.tr/~semen/dist/test/multimedia/graphics/graphics.tar
  \end{verbatim}
\end{itemize}
\item After installation iksemel package:

Observe that the below commands run without any problem.
\begin{verbatim}
 # wget http://cekirdek.pardus.org.tr/~semen/dist/test/library/component.xml
 # ikslint -s component.xml
 # iksperf -a component.xml 
\end{verbatim}

\item After installation xulrunner and xulrunner-devel packages:
\begin{itemize}
\item Do office-eng.pdf openoffice test.
\item Do network-eng.pdf firefox test.
\item Do network-eng.pdf gecko-mediaplayer test.
\item Do multimedia-eng.pdf vlc-firefox test.
\end{itemize}

\item After installation libvorbis package:

Do multimedia-eng.pdf vorbis-tools test.

\item After installation xerces-c package:

Download the following packages into the same directory.
\begin{verbatim}
# wget http://cekirdek.pardus.org.tr/~semen/dist/test/library/shiporder.xml
# wget http://cekirdek.pardus.org.tr/~semen/dist/test/library/shiporder.xsd
# wget http://cekirdek.pardus.org.tr/~semen/dist/test/library/test-xerces-c.sh
\end{verbatim}

Run ./test-xerces-c.sh file and observe that the result did not return any error.
\begin{verbatim}
# chmod 755 test-xerces-c.sh
# ./test-xerces-c.sh | less
\end{verbatim}

\item After installation apr and apr-util package:

Do programming-eng.pdf subversion test.

\item After installation portaudio package:

Do multimedia-eng.pdf qpitch test.

\item After installation libv4l package: 

(If you have a webcam you can test this package)

Close all webcam related applications and run the following command and observe that the webcam test is done without any problem:
\begin{verbatim}
 test-webcam
\end{verbatim}

\item After installation qca2 and qca2-apidocs packages:
\begin{itemize}
 \item Run the following command:
\begin{verbatim}
# qcatool2 plugins 
\end{verbatim}
\item Do network-eng.pdf konversation test.
\end{itemize}


\item After installation icu4c package:

Do programming-eng.pdf PyICU test.

\item After installation raptor and redland packages:

Do office-eng.pdf openoffice writer test.

Do desktop-eng.pdf kdegraphics test.

\item After installation libnice package:

Do network-eng.pdf pidgin test.

\item After installation libtdb package:

İnstall samba package and srat samba from service manager.

Observe that the below commands work without any problem.
\begin{verbatim}
 # tdbtool
 # create test
 # open test 
 # insert testkey testdata
 # show testkey
\end{verbatim}
\item After installation qzion package:

Do library-eng.pdf qedje test.

\end{enumerate}

\end{document}

