\documentclass[a4paper,10pt]{article}
\usepackage[turkish]{babel}
\usepackage[utf8]{inputenc}
\usepackage[left=1cm,top=1cm,right=2cm,bottom=2cm]{geometry}

\title{Science Component Test Cases}
\author{Semen Cirit}

\renewcommand{\labelenumi}{\arabic{enumi}.}
\renewcommand{\labelenumii}{\arabic{enumi}.\arabic{enumii}.}
\renewcommand{\labelenumiii}{\arabic{enumi}.\arabic{enumii}.\arabic{enumiii}.}
\renewcommand{\labelenumiv}{\arabic{enumi}.\arabic{enumii}.\arabic{enumiii}.\arabic{enumiv}.}

\begin{document}

\maketitle
\section{Electronics sub component}
\begin{enumerate}
 \item Following packages subject to installation test:
\begin{verbatim}
 gpsim
\end{verbatim}

\end{enumerate}


\section{Gis sub component}
\begin{enumerate}
 \item After installation gpsd and libgps packages:

(If you have a gps you can test this package.)

Plug your gps then start gpsd service from service manager. In order to be sure run the below command.
\begin{verbatim}
 service gpsd status
\end{verbatim}


\end{enumerate}


\section{Astronomy sub component}
\begin{enumerate}
 \item After installation stellarium package:

Open the application from Kmenu and observe that it can open without any problem.
\end{enumerate}

\section{Chemistry sub component}
\begin{enumerate}
 \item After installation openbabel package:

Run the below commands. Observe that the test.smi file has "c1cccc(c1C(=O)O)OC(=O)C·C9H8O4" information.
\begin{verbatim}
 # babel -H sdf
 # wget http://cekirdek.pardus.org.tr/~semen/dist/test/science/aspirin.sdf
 # babel -isdf 'aspirin.sdf' -osmi 'test.smi'
 # vi test.smi
\end{verbatim}

\end{enumerate}

\section{Mathematics sub component}
\begin{enumerate}
\item After installation rkward package:

Open the application from Kmenu and click the Plots $\rightarrow$ Barplot. Select an item from the list and then click submit and apply it. Observe that the related graphic is opened without any problem.

\item After installation wxMaxima package:

Open the application from Kmenu. Do some mathematical application and observe the applications can be done without any problem.

\item After installation maxima package:

Observe that the following commands run without any problem.
\begin{verbatim}
 # maxima
 144*17 - 9;
 144^25;
\end{verbatim}

\item Following packages subject to installation test:
\begin{verbatim}
gfan 
\end{verbatim}

\end{enumerate}

\section{Robotics sub component}
\begin{enumerate}
 \item After installation opencv package: 
(If you have a webcam you can test this package.)

Plug the webcam then run the below commands. observe that the webcam window is opened.
\begin{verbatim}
# wget http://svn.pardus.org.tr/projeler/facelock/pardus.py
# wget http://svn.pardus.org.tr/projeler/facelock/pardus.png
# python pardus.py
\end{verbatim}


\end{enumerate}

\end{document}

