\documentclass[a4paper,10pt]{article}
\usepackage[turkish]{babel}
\usepackage[utf8]{inputenc}
\usepackage[left=1cm,top=1cm,right=2cm,bottom=2cm]{geometry}

\title{System Component Test Cases}
\author{Semen Cirit}

\renewcommand{\labelenumi}{\arabic{enumi}.}
\renewcommand{\labelenumii}{\arabic{enumi}.\arabic{enumii}.}
\renewcommand{\labelenumiii}{\arabic{enumi}.\arabic{enumii}.\arabic{enumiii}.}
\renewcommand{\labelenumiv}{\arabic{enumi}.\arabic{enumii}.\arabic{enumiii}.\arabic{enumiv}.}

\begin{document}

\maketitle


\section{Devel sub Component}
\begin{enumerate}
 \item Following packages subject to installation test:
\begin{verbatim}
 xtrans
 automake
 dietlibc 
 quilt
\end{verbatim}
 \item After installation  icecream and icecream scheduler packages:

Start icecream service from Service manager.

To learn whether service is started or not, execute the command below.
 \begin{verbatim}
   # service icecream status
 \end{verbatim}

\end{enumerate}


\section{Base sub Component}

\begin{enumerate}
\item After installation python package:
\begin{itemize}
 \item Do the system-eng.pdf pisi package test.
 \item Do the programming-eng.pdf sympy package test.
 \item Do the programming-eng.pdf python-iptables package test.
\end{itemize}


\item After installation  openssl package:

Observe that commands below run without any errors:
\begin{verbatim}
  # openssl ciphers -v 
  # openssl ciphers -v -tls1
  # openssl speed
  # openssl req  -new -newkey rsa:1024 -nodes -keyout mykey.pem -out myreq.pem
  // verify signature
  # openssl req -in myreq.pem -noout -verify -key mykey.pem
  // check info
  # openssl req -in myreq.pem -noout -text

\end{verbatim}


\item After installation  usbutils package:

Observe that commands below run without any errors:
\begin{verbatim}
# usb-devices
# lsusb
\end{verbatim}


\item After installation  udev package:

Restart your computer and then check that: it opens without any errors. 

Observe that sound, camera, mount, display works without any errors.
\item Packages below will only be tested by installing them.
\begin{verbatim}
e2fsprogs 
\end{verbatim}
\item After installation  module-init-tools package:

Restart your computer:
check that: Sound, wireless, bluetooth, camera works without any errors.

Observe that commands below run without any errors:
\begin{verbatim}
 # lsmod
 # modinfo ahci
\end{verbatim}


\item After installation  dnsmasq package:

\begin{itemize}
 \item Start dnsmasq from your service manager.
 \item From network manager, stop your connection and restart your connection.
 \item Run the command below and  check that: query time is showed without any errors.
\begin{verbatim}
 # dig http://archlinux.org | grep "Query time"
\end{verbatim}

\end{itemize}


\item After installation  file package:

\begin{verbatim}
 # wget http://cekirdek.pardus.org.tr/~semen/dist/test/office/openoffice/test_oodraw.mng
 # wget http://cekirdek.pardus.org.tr/~semen/dist/test/office/openoffice/test_oodraw.odg
 # wget http://cekirdek.pardus.org.tr/~semen/dist/test/office/openoffice/test_oodraw.jpg
 # wget http://cekirdek.pardus.org.tr/~semen/dist/test/office/openoffice/test_oodraw.gif
 # wget http://cekirdek.pardus.org.tr/~semen/dist/test/office/openoffice/test_oodraw.png
 # wget http://cekirdek.pardus.org.tr/~semen/dist/test/office/openoffice/test_oodraw.tif
 # wget http://cekirdek.pardus.org.tr/~semen/dist/test/office/openoffice/test_oowriter.txt
 # wget http://cekirdek.pardus.org.tr/~semen/dist/test/office/openoffice/test_oodraw.ps
 # wget http://cekirdek.pardus.org.tr/~semen/dist/test/office/openoffice/
   test_openoffice-extension-pdfimport.pdf
\end{verbatim}

Run the command below with the files above, check that: it finds file types without any error.
\begin{verbatim}
 # file <dosya adı>
\end{verbatim}

\item After installation  mudur package:

\begin{itemize}
  \item Restart your computer and check that: system is opened without any errors.
 \item Press Ctrl+Alt+F1 and switch to system console and check that: your system's language and keyboard settings are same with the ones before.
  \item Observe that files locale, language, keymap, which are in /etc/mudur/ directory  are synchronized with your system language and keyboard.
 \item Observe that pisi commands run without any errors. 

\end{itemize}
\item After installation  tiff package:
\begin{verbatim}
 # wget http://cekirdek.pardus.org.tr/~semen/dist/test/desktop/kde/base/doga.tiff
 # wget http://cekirdek.pardus.org.tr/~semen/dist/test/desktop/kde/base/istanbul.tiff
\end{verbatim}

By right clicking on the images,open them with gwenview, kolourPaint, gimp, showfoto and check that: They can be opened without any errors.
\item After installation  pisi package:
\begin{itemize}
 \item Do package-manager-eng.pdf test cases.
 \item Do history-manager-eng.pdf test cases.
\end{itemize}
\item After tha install of baselayout package:
\begin{itemize}
 \item Shutdown your computer, check that: it shutdowns without any errors.
 \item Restart your computer, check that: it restarts without any errors.
 \item For 2009:
  \begin{verbatim}
   # pisi blame baselayout
  \end{verbatim}
      For 2008: http://svn.pardus.org.tr/pardus/2008/stable/system/base/baselayout/pspec.xml  look into the lastly added comment to history tag in this link.

   For both of the situations, check that: the user that's mentioned in the comments is added into the /etc/passwd file.

\end{itemize}
\item After installation  libxml2 package:

\begin{itemize}
\item Observe that the command below creates a catalog.
  \begin{verbatim}
   #  xmlcatalog --create
  \end{verbatim}
\item Run multimedia-eng.pdf avidemux-qt, avidemux and inkscape tests.
\end{itemize}
\item After installation  curl package:

\begin{itemize}
\item Observe that http://pardus.org.tr this address's content can be taken without an any error.
\begin{verbatim}
# wget http://cekirdek.pardus.org.tr/~semen/dist/test/system/base/test_curl.php
# php test_curl.php
\end{verbatim}

\item Run network-eng.pdf sylpheed tests.
\end{itemize}

\item After installation  glib2 package:
\begin{itemize}
 \item Do system-eng.pdf openssh package test.
\item Do system-eng.pdf getext package test.
\end{itemize}

\item After installation  gettext package:

check that: The command below creates "network-manager.pot" file.
\begin{verbatim}
 # svn co http://svn.pardus.org.tr/uludag/trunk/kde4/network-manager/
 # cd network-manager/manager
 # rm -rf po
 # mkdir po
 # xgettext setup.py 
 # ./setup.py update_messages
\end{verbatim}


\item After installation  openssh package:

Start openssh from service manager and check that: in the output of command below, openssh is working:
\begin{verbatim}
 # service list 
\end{verbatim}

\item After installation  mkinitramfs package:

Restart your computer. Observe that it is opened without any errors.

In /boot/ directory check that: the current kernel's initramfs file exists.

\item pardus-python package will only be tested by installing.

\end{enumerate}
\section{Service sub Component}
\begin{enumerate}
 \item After installation  memcached package:

  Do programming-eng.pdf python-memcached tests. 
\end{enumerate}



\end{document}

