\documentclass[a4paper,10pt]{article}

 \usepackage[left=1cm,top=1cm,right=2cm,bottom=2 cm]{geometry}
\title{User Manager Test Cases}
\author{Semen Cirit}

\renewcommand{\labelenumi}{\arabic{enumi}.}
\renewcommand{\labelenumii}{\arabic{enumi}.\arabic{enumii}.}
\renewcommand{\labelenumiii}{\arabic{enumi}.\arabic{enumii}.\arabic{enumiii}.}
\renewcommand{\labelenumiv}{\arabic{enumi}.\arabic{enumii}.\arabic{enumiii}.\arabic{enumiv}.}

\begin{document}

\maketitle
\begin{enumerate}

\item Try to open user manager from user settings

\item Try to open user manager from Kmenu.

\item Add a new user

    Execute the following command:
    \begin{verbatim}
        $ getent passwd 
    \end{verbatim}
    Observe whether the user is added.

    \begin{enumerate}
    \item Try to change password
        \begin{enumerate}
        \item Write a new password to password part and retype part.
        \item Write a new password, and write a different password to retype part.

                Observe that it gives a warning about it.
        \end{enumerate}
    \end{enumerate}

    \item Enable root permissions.

          Switch user to newly added user, then try to be root with this user.
        Observe that you can be root.
    \item Disable root permissions.

        Switch user to newly added user, then try to be root with this user.
    
        Observe that you couldn't be root.

    \item Give an authorization.

        Execute the following command: (being root)
    \begin{verbatim}
        # cat /var/lib/PolicyKit/user-<username>.auths
    \end{verbatim}
        Observe whether the authorization is given to this user.

    
\item Try to add a new group.

     Execute the following command:
\begin{verbatim}
     cat /etc/group
 \end{verbatim}
     observe whether the group is added.

\item Add user to this new group 

          Execute the following command:
    \begin{verbatim}
        $ groups <username> 
    \end{verbatim}

        and observe the results

\item Try to remove a group.

\begin{enumerate}
    \item Execute the following command:

\begin{verbatim}
     $ getent group
\end{verbatim} 

     Observe whether the group is removed.

    \item Observe the user who was added to this group.

     Execute the following command:
\begin{verbatim}
     $ groups <username>·
\end{verbatim} 
     Observe that the user is not a member of this group anymore.
\end{enumerate}

\item Remove user from a group.

       Execute the following command:
    \begin{verbatim}
        $ groups <username> 
    \end{verbatim}
        and observe the results

\item Try to change informations of the newly aded user.

\item Try to remove the user.

      Execute the following command:
\begin{verbatim}
     $ getent passwd
\end{verbatim}
     Observe whether the user is removed.

\item Try to list all users.
\item Try to list all groups.

\item During some operation, cancel the authorization window.

After operation canceled, observe that the user manager remain in previous state.

\item During an operation, select always remember user password.

Make an other operation from user manager.

Observe that the autorization is ignored.


\end{enumerate}

\end{document}


\end{enumerate}

\end{document}


