\documentclass[a4paper,10pt]{article}
\usepackage[turkish]{babel}
\usepackage[utf8]{inputenc}
\usepackage[left=1cm,top=1cm,right=2cm,bottom=2cm]{geometry}

\title{Util Component Test Cases}
\author{Semen Cirit}

\renewcommand{\labelenumi}{\arabic{enumi}.}
\renewcommand{\labelenumii}{\arabic{enumi}.\arabic{enumii}.}
\renewcommand{\labelenumiii}{\arabic{enumi}.\arabic{enumii}.\arabic{enumiii}.}
\renewcommand{\labelenumiv}{\arabic{enumi}.\arabic{enumii}.\arabic{enumiii}.\arabic{enumiv}.}

\begin{document}

\maketitle
\section{Archive sub Component}
\begin{enumerate}
 \item After installation  lrzip package:

Observe that the following commands first compress then uncompress the test\_lrzip file.
\begin{verbatim}
 # wget http://cekirdek.pardus.org.tr/~semen/dist/test/util/test_lrzip
 # lrzip test_lrzip
 # mkdir test
 # lrzip -d test_lrzip.lrz -O test/
\end{verbatim}


\end{enumerate}


\section{Crypt sub component}
\begin{enumerate}
 \item After installation  mcrypt package:

Observe that commands below run without any errors.
\begin{verbatim}
 # mcrypt --list
 # wget http://cekirdek.pardus.org.tr/~semen/dist/test/util/test_mcrypt
 # mcrypt -a blowfish test_mcrypt
 # mcrypt -d test_mcrypt.nc
 # vi test_mcrypt
\end{verbatim}


\end{enumerate}


\section{Antivirus sub component}
\begin{enumerate}
\item After installation  Klamav package:

Copy the file below into a directory. 
\begin{verbatim}
# wget https://secure.eicar.org/eicar.com.txt
\end{verbatim}

By using Klamav application, scan this directory, and check that: Klamav finds the virus and wants to take it into quarantine.

\item After installation  Clamav package:

Copy the file below into a directory. 
\begin{verbatim}
# wget https://secure.eicar.org/eicar.com.txt
# clamscan eicar.com.txt
\end{verbatim}

Observe that second command above can detect virus.

\end{enumerate}
\section{Admin sub component}
\begin{enumerate}
 \item After installation  phpmyadmin package:
\begin{itemize}
 \item Start Apache and mysql services from service manager. Run the command below and make the root password "test":
\begin{verbatim}
 mysqladmin -u root password 'test'
\end{verbatim}

 \item http://localhost/phpmyadmin/ go to this address by using firefox. (For username write root, for password  write test)
 \item Check that: Mysql connection page is opened without any errors.
\end{itemize}



 \item After installation  iotop package:

Run the command below and check that: It lists I/O band width of all the applications that's running on the system.
\begin{verbatim}
 # iotop
\end{verbatim}

\end{enumerate}
\section{Shell sub component}
\begin{enumerate}
 \item After installation  bash-completion package:

Check that: The command below runs without any errors.
\begin{verbatim}
 # pisi --help
\end{verbatim}

\item After installation  command-not-found package:

If Amsn package is not installed in your system, when you run the command below:
\begin{verbatim}
 # amsn
\end{verbatim}

check that: It gives the error messega below:
\begin{verbatim}
'amsn' uygulaması sisteminizde kurulu değil. Bu paketi, paket yöneticisini kullanarak ya da aşağıdaki komutu çalıştırarak kurabilirsiniz:
sudo pisi it amsn
bash: amsn: command not found
\end{verbatim}

\end{enumerate}
\section{Misc sub component}
\begin{enumerate}
 \item After installation  fslint package:

Check that: It can be opened from KMenu.

Copy two files into two different directories and add these two different directories into the application, Click into copied files and press find button and check that: Copied files are listed.
 \item After installation  ltrace package:

Check that: The command below runs without any errors:
\begin{verbatim}
 # ltrace ls
\end{verbatim}
\item After installation  elfutils package:

Run util-tr.pdf ltrace test.
\end{enumerate}



\end{document}

